\documentclass[fontsize=12pt, paper=letter]{scrlttr2}

% Dont forget to read the KOMA-Script documentation, scrguien.pdf

\setkomavar{fromname}{Dr.\ Garrett Smith} % your name
\setkomavar{fromaddress}{Department of Linguistics\\
    University of Potsdam\\
    Potsdam, Germany}

\setkomavar{signature}{Dr.\ Garrett Smith} % printed after the \closing
\renewcommand{\raggedsignature}{\raggedright} % make the signature ragged right

\setkomavar{subject}{} % subject of the letter

%\usepackage[backend=biber,useprefix=true, style=apa,%citestyle=numeric,firstinits=true,
%url=false,doi=false,%sortcites=true,
%sorting=nyt,eprint=false]{biblatex}
%\DeclareNameAlias{author}{last-first}
%\addbibresource{master.bib}

\begin{document}
\begin{letter}{Dr. Edward Gibson\\
    Editor\\
    Open Mind}

\opening{Dear Dr. Gibson,}

I would like to submit for your consideration the attached manuscript, entitled
\emph{Mparse: A new framework for self-organized, incremental sentence
comprehension}.

The paper presents a computational model of word-by-word sentence parsing,
called \emph{mparse}, in which syntactic structures for whole sentences
assemble themselves out of word-word dependency links. Self-organization as
theory of parsing goes back at least to Kempen and Vosse (1989;
\emph{Connection Science 1}(3)), but previous implementations have faced a
number of shortcomings. The new model seeks to alleviate these issues to
make self-organized parsing a more easily and broadly testable theory in
psycholinguistics. I test the model on garden path, local coherence, and
ambiguity advantage effects and find that it reproduces human reading time
behavior. I believe the manuscript will be of interest to the \emph{Open
Mind} readership as it provides a mathematically tractable implementation
of self-organization that makes novel experimental predictions and can form
the basis for future comparisons with other theories of sentence
processing.

All the data and code relating to the paper are available from the following
link: https://osf.io/k6rnx/.

Suggested reviewers:
\begin{itemize}
\item Lena Jäger: jaeger@cl.uzh.ch
\item Emily Morgan: eimorgan@ucdavis.edu
\item Lars Konieczny: lars@cognition.uni-freiburg.de
\item Paul Smolensky: smolensky@jhu.edu
\item Roger Levy: rplevy@mit.edu
\end{itemize}

I look forward to hearing from you. 

\closing{Sincerely,} %eg. Regards


\end{letter}
\end{document}
